Analytic Doppler Imaging

### 2019-08-19 tex/ms.tex
finalllllly

\subsection{Solution for the intensity}
\label{sec:solve_y}
For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{S} =
        \begin{pmatrix}
        \quadquad\bvec{s}\quadquad & &            &            &  \\
        & \quadquad\bvec{s}\quadquad &            &            &  \\
        &            & \quadquad\bvec{s}\quadquad &            &  \\
        &            &            & \quadquad\bvec{s}\quadquad &  \\
        &            &            &               & \ddots
        \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column
vector $\bvec{s}$ $N$ times in blocks along the main diagonal. 
%
Before we solve this equation for $\bvec{y}$, we note that in practice
it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
harmonic, $y_0$, to unity. After all, this coefficient is not directly
constrained by the data, as it merely sets the baseline intensity on the
surface of the star and is therefore formally degenerate with the stellar 
luminosity (which also cannot be directly inferred from the data). This
choice further ensures a mean baseline of unity for the model 
vector $\mathbf{f}$. We may therefore write
%
\begin{align}
    \label{eq:inverse:fy1}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{s}_\bvec{0}
    \,
    +
    \,
    \Doppler
    \,
    \bvec{S_1}
    \,
    \bvec{y}_\bvec{1}
    \quad,
\end{align}
%
where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical 
harmonic coefficients of degree $l \ge 1$.

@@

\subsection{Solution for the spectrum}
\label{sec:solve_s}
If, on the other hand, the spatial intensity profile is known, the
model for the flux vector may be written in terms of the spectrum $\bvec{s}$
as
%
\begin{align}
    \label{eq:inverse:fs}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{Y}
    \,
    \bvec{s}
    \quad,
\end{align}
%
where
%
\begin{align}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{Y} =
        \begin{pmatrix}
            y_0\, \bvec{I}_{K'} \\
            y_1\, \bvec{I}_{K'} \\
            y_2\, \bvec{I}_{K'} \\
            y_3\, \bvec{I}_{K'} \\
            \cdots
        \end{pmatrix}
\end{align}
%
is a $(NK' \times K')$ matrix constructed by vertically stacking
$N$ $(K' \times K')$ identity matrices, each multiplied by the
corresponding coefficient of $\bvec{y}$. Given
prior mean $\boldsymbol{\mu}_\mathbf{s}$ and covariance
$\boldsymbol{\Lambda}_\mathbf{s}$ on $\mathbf{s}$, the MAP solution
is given by
%
\begin{align}
    \label{eq:inverse:shat}
    \bvec{\hat{s}} &= 
    \boldsymbol{\Sigma}_\mathbf{\hat{s}}
    \left(
        \bvec{Y}^\top\Doppler^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \bvec{f}
        +
        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1} \boldsymbol{\mu}_\mathbf{s}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:inverse:scov}
    \boldsymbol{\Sigma}_\mathbf{\hat{s}} &= 
    \left(
        \bvec{Y}^\top\Doppler^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \Doppler\bvec{Y}
        +
        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1}
    \right)^{-1}
    \quad.
\end{align}

@@

\section{Bells and Whistles}
\label{sec:bells}

@@

\subsection{Limb darkening}
Hello.

@@

    \caption{Notation used in this paper \xxx{mostly complete up to sec 5}} 

@@

@@

@@

    $\bvec{s}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\

@@

@@

>>>>

\subsection{Solution for the intensity}
\label{sec:solve_y}
For a fixed, spatially constant rest-frame spectrum $\bvec{s}$, the model
for the flux vector may be written as
%
\begin{align}
    \label{eq:inverse:fy}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{S}
    \,
    \bvec{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:S}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{S} =
        \begin{pmatrix}
        \quadquad\bvec{s}\quadquad & &            &            &  \\
        & \quadquad\bvec{s}\quadquad &            &            &  \\
        &            & \quadquad\bvec{s}\quadquad &            &  \\
        &            &            & \quadquad\bvec{s}\quadquad &  \\
        &            &            &               & \ddots
        \end{pmatrix}
\end{align}
%
is a $(NK' \times N)$ block matrix constructed by repeating the column
vector $\bvec{s}$ $N$ times in blocks along the main diagonal. 
%
Before we solve this equation for $\bvec{y}$, we note that in practice
it is convenient to fix the coefficient of the $Y_{0,0}$ spherical
harmonic, $y_0$, to unity. After all, this coefficient is not directly
constrained by the data, as it merely sets the baseline intensity on the
surface of the star and is therefore formally degenerate with the stellar 
luminosity (which also cannot be directly inferred from the data). This
choice further ensures a mean baseline of unity for the model 
vector $\mathbf{f}$. We may therefore write
%
\begin{align}
    \label{eq:inverse:fy1}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{s}_\bvec{0}
    \,
    +
    \,
    \Doppler
    \,
    \bvec{S_1}
    \,
    \bvec{y}_\bvec{1}
    \quad,
\end{align}
%
where the vector $\bvec{s_0}$ denotes the first column of $\bvec{S}$,
the matrix $\bvec{S_1}$ denotes the remaining columns of $\bvec{S}$, and
$\bvec{y_1}$ is the quantity we wish to solve for: the vector of spherical 
harmonic coefficients of degree $l \ge 1$.

@@

\subsection{Solution for the spectrum}
\label{sec:solve_s}
If, on the other hand, the spatial intensity profile is known, the
model for the flux vector may be written in terms of the spectrum $\bvec{s}$
as
%
\begin{align}
    \label{eq:inverse:fs}
    \bvec{f}
    &=
    \Doppler
    \,
    \bvec{Y}
    \,
    \bvec{s}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:inverse:Y}
    \setstackgap{L}{1.25\baselineskip}
    \bvec{Y} =
        \begin{pmatrix}
            y_0\, \bvec{I}_{K'} \\
            y_1\, \bvec{I}_{K'} \\
            y_2\, \bvec{I}_{K'} \\
            y_3\, \bvec{I}_{K'} \\
            \cdots
        \end{pmatrix}
\end{align}
%
is a $(NK' \times K')$ matrix constructed by vertically stacking
$N$ $(K' \times K')$ identity matrices, each multiplied by the
corresponding coefficient of $\bvec{y}$. Given
prior mean $\boldsymbol{\mu}_\mathbf{s}$ and covariance
$\boldsymbol{\Lambda}_\mathbf{s}$ on $\mathbf{s}$, the MAP solution
is given by
%
\begin{align}
    \label{eq:inverse:shat}
    \bvec{\hat{s}} &= 
    \boldsymbol{\Sigma}_\mathbf{\hat{s}}
    \left(
        \bvec{Y}^\top\Doppler^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \bvec{f}
        +
        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1} \boldsymbol{\mu}_\mathbf{s}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:inverse:scov}
    \boldsymbol{\Sigma}_\mathbf{\hat{s}} &= 
    \left(
        \bvec{Y}^\top\Doppler^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \Doppler\bvec{Y}
        +
        {\boldsymbol{\Lambda}_\mathbf{s}}^{-1}
    \right)^{-1}
    \quad.
\end{align}

@@

\section{Further considerations}
\label{sec:bellswhistles}

@@

\subsection{Limb darkening}
\label{sec:ld}
Thus far we have avoided mention of limb darkening, whose effect
on the observed spectrum can often be significant. A proper treatment of
limb darkening requires solution of radiative transfer equations and
should account for the temperature and composition gradients in the
stellar atmosphere. However, in the spirit of data-driven inference, we 
may simply weight the spatial component of our map by the limb darkening
profile of the star, which can either be imposed or learned from the data.

@@

    \caption{Notation used in this paper} 

@@

    $\bvec{b}$               & flux baseline vector                                  & Equation~(\ref{eq:norm:b})\\
    $\bvec{B}$               & block matrix representation of $\bvec{b}$             & Equation~(\ref{eq:norm:b})\\

@@

    $\bvec{S}$               & block matrix representation of $\bvec{s}$             & Equation~(\ref{eq:inverse:S})\\

@@

    $\bvec{y}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\

@@

    $\bvec{Y}$               & block matrix representation of $\bvec{y}$             & Equation~(\ref{eq:inverse:Y})\\

@@

    $\boldsymbol{\mu}$       & prior mean vector                                     & \\
